### 2022-11-14 NSF2022/Description/summary.tex
working on overview

\subsection*{Overview}
\vspace{-0.1in}
This proposal aims to advance mathematical modeling and analysis of
collective dynamics of amphiphilic self-assembly. Amphiphilic particles
such as lipid molecules possess both hydrophobic and hydrophilic
surfaces and self-assemble into meso/macroscopic structures such as
micelles and bilayers of lipids. Experimentalists model self-assembly
using Janus particles—spherical particles possessing a biphasic material
label on either hemisphere. Janus particles have been widely used in
soft matter physics as a model amphiphilic colloid and can be designed
for catalytic activity or stimuli-responsive smart materials.

Hydrophobic surfaces experience a nonadditive long-range attraction
called the hydrophobic force. This force is a major source of
nonspecific interactions in biology and soft matter. Despite its
ubiquity, theoretical developments explaining its basic underlying
principles have come relatively late. Motivated by its broad
applicability, the PIs recently developed a novel and intuitive
mathematical model, called the hydrophobic attraction potential model,
based on the linear response of water to surface perturbations. This
model was used to show, for the first time, self-assembly of Janus
particles into vesicle-like structures using a partial differential
equation-based particle interaction.

The PIs propose to apply their hydrophobic attraction potential model to
the self-organization dynamics of Janus particles. They aim to
generalize the linear-response model to more general hydrophobic
interactions, and numerically implement these interactions using
integral equation formulations. Finally, they will investigate and
simulate hydrophobic interactions in the presence of electric charge and
ions. The unifying aspects of the project are establishing a platform
for efficiently simulating the collective dynamics at large scales, and
the focusing on rigorous, mathematical analysis of the underlying model
equations and complicated geometries. The project supports undergraduate
and graduate student collaborators.

>>>>

\subsection*{Overview}
\vspace{-0.1in}
This proposal aims to advance mathematical modeling and analysis of
collective dynamics and self-assembly arising from attractive
interactions between dipolar/nematic particles in a suspension. For
example, the organization of lipids and proteins in vesicles is crucial
to design effective drug carriers. Physicists model such a self-assembly
using particles possessing a biphasic material label on either half,
with one more hydrophobic than the other. Hydrophobic surfaces
experience a nonadditive long-range attraction called the hydrophobic
force. This force is a major source of nonspecific interactions in
biology and soft matter. Despite its ubiquity, theoretical developments
explaining its basic underlying principles have come relatively late.
Motivated by its broad applicability, the PIs recently developed a novel
and intuitive mathematical model, called the hydrophobic attraction
potential model, based on the linear response of water to surface
perturbations. This model was used to show, for the first time,
self-assembly of such bipolar particles into vesicle-like structures
using moving domain elliptic partial differential equations.

%This proposal aims to advance mathematical modeling and analysis of
%collective dynamics of amphiphilic self-assembly. Amphiphilic particles
%such as lipid molecules possess both hydrophobic and hydrophilic
%surfaces and self-assemble into meso/macroscopic structures such as
%micelles and bilayers of lipids. Experimentalists model self-assembly
%using Janus particles—spherical particles possessing a biphasic material
%label on either hemisphere. Janus particles have been widely used in
%soft matter physics as a model amphiphilic colloid and can be designed
%for catalytic activity or stimuli-responsive smart materials.

%Hydrophobic surfaces experience a nonadditive long-range attraction
%called the hydrophobic force. This force is a major source of
%nonspecific interactions in biology and soft matter. Despite its
%ubiquity, theoretical developments explaining its basic underlying
%principles have come relatively late. Motivated by its broad
%applicability, the PIs recently developed a novel and intuitive
%mathematical model, called the hydrophobic attraction potential model,
%based on the linear response of water to surface perturbations. This
%model was used to show, for the first time, self-assembly of Janus
%particles into vesicle-like structures using a partial differential
%equation-based particle interaction.

The PIs propose to apply their hydrophobic attraction potential model to
more general self-organization dynamics. They aim to generalize the
linear-response model to more general hydrophobic interactions, and
numerically implement these interactions using integral equation
formulations. Finally, they will investigate and simulate hydrophobic
interactions in the presence of electric charge and ions. The unifying
aspects of the project are establishing a platform for efficiently
simulating the collective dynamics at large scales, and the focusing on
rigorous, mathematical analysis of the underlying model equations and
complicated geometries. The project supports undergraduate and graduate
student collaborators.

### 2022-11-14 NSF2022/SupplementaryDocs/excludedreviewers.tex
working on overview

\noindent
\today \\ \\
Dear Program Officer:
\\ \\
Professor Alex Donev (donev@courant.nyu.edu) is a competitor that is
working on similar problems to those described in the proposal entitled
``Collaborative Proposal: Self-organization modeled by moving domain
elliptic PDEs". We request that they are not chosen to review the
proposal.
\\ \\
Sincerely, \\ \\
Bryan Quaife, Rolf Ryham, and Yuan-Nan Young

>>>>

\noindent
\today \\ \\
Dear Program Officer:
\\ \\
Professors Alex Donev (donev@courant.nyu.edu) and Yoichiro Mori
(y1mori@sas.upenn.edu) are competitors that are working on similar
problems to those described in the proposal entitled ``Collaborative
Proposal: Self-organization modeled by moving domain elliptic PDEs". We
request that they are not chosen to review the proposal.
\\ \\
Sincerely, \\ \\
Bryan Quaife, Rolf Ryham, and Yuan-Nan Young
